\textbf{ Discovery of a disrupting open cluster far into the Milky Way halo:\\ a recent star formation event in the leading arm of the Magellanic stream?}

### 2019-06-25 ms.tex
typo

Other possible formation scenarios for \clustername\ do not help to resolve these issues.
One possible alternative scenario is that the \clustername\ birth cloud was unassociated with the MS and instead a lone HVC.
However, this still raises questions about what triggered the star formation, given that other HVCs in the Milky Way are observed to be devoid of stars (e.g., \citalt{Stark:2015}).
Another possible origin for \clustername\ is that it formed from gas stripped from a fully-destroyed dwarf galaxy (an unknown satellite of the Magellanic Clouds).
However, the cluster appears to have a single, very young stellar population, and other, comoving, older stars have not been found associated with the LA in this region.

>>>>

Other possible formation scenarios for \clustername\ do not help to resolve these issues.
One possible alternative scenario is that the \clustername\ birth cloud was unassociated with the MS and instead a lone HVC.
However, this still raises questions about what triggered the star formation, given that other HVCs in the Milky Way are observed to be devoid of stars (e.g., \citealt{Stark:2015}).
Another possible origin for \clustername\ is that it formed from gas stripped from a fully-destroyed dwarf galaxy (an unknown satellite of the Magellanic Clouds).
However, the cluster appears to have a single, very young stellar population, and other, comoving, older stars have not been found associated with the LA in this region.
